Classical probability measures as pullback of quantum probability measures?

### 2022-05-12 pullback.tex
pullback.lyx On Fri, May 13, 2022 at 4:10 AM Yu-Tsung Tai <yuttai@alumni.iu.edu>

>>>>

\subsection{The Source of Probability and Contextuality}

One of reason why we need probability is because we don't know the
detail to generate the outcomes. For example, a number might be deterministically
generated by a random number generator, but looks random for whom
don't know the seed and the algorithm. One might calculate whether
a flipped coin will be head up or tail up, but flipping coin looks
like a random process for whom don't know the initial condition. Whether
the randomness of a quantum process is also due to lack of knowledge
was asked by Einstein, Podolsky, and Rosen (EPR)~\cite{EPR1935,peres1995quantum,544199,Mermin2007}.
In the language of our previous examples, they guess there might be
some unknown physical laws such that if we know the initial condition
of the particle we could predict with certain that one of the outcomes
$\omega_{z}\in\Omega_{z}$ will happen.

EPR's question apparently looks hard, but could be explained if we
assume the predictions among these processes are correlated and consider
more experimental processes. To simplify the later discussion, we
will represent the certain outcome $\omega_{z}$ as its characteristic
function $\chi_{z}:\Omega_{z}\rightarrow\left\{ 0,1\right\} $ defined
by
\begin{equation}
\chi_{z}\left(\omega\right)=\begin{cases}
1 & \textrm{if }\omega=\omega_{z}\,;\\
0 & \textrm{if }\omega\ne\omega_{z}\,,
\end{cases}
\end{equation}
and we will represent the hypothetical certain prediction of experiment
$\mu_{x}$ as another characteristic function $\chi_{x}:\Omega_{x}\rightarrow\left\{ 0,1\right\} $.
Notice that Eq.~(\ref{eq:mu0-equal-mu1}) states the probability
of event $\left\{ \ket{2}\right\} $ should be the same no matter
which process to generate the outcomes. We may generalize this idea
to assume the characteristic functions of the common outcomes to be
the same, i.e., 
\begin{equation}
\chi_{z}\left(\ket{2}\right)=\chi_{x}\left(\ket{2}\right)\,.\label{eq:equality-among-chi}
\end{equation}
